Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2012-12-27 docs/tex/draft.tex
Pareto frontier code
Debugging a case wherein multiple sequences with the same energy cause the CMRF decoding to fail

\subsubsection{Converting a HMM to CMRF}
It is possible to reparameterize an HMM so that it now becomes a CMRF. The partition function $Z$ of the newly constructed CMRF equals 1 corresponding to a probability distribution., However there is

\subsection{Combining the CMRF to a HMM}

@@

>>>>

\subsubsection{Converting a HMM to CMRF}
It is possible to reparameterize an HMM so that it now becomes a CMRF. The partition function $Z$ of the newly constructed CMRF equals 1 corresponding to a probability distribution.

\subsection{Combining CMRFs to get a TMRF}

@@

\paragraph{Multiple sequence Same Energy} :  Currently the cvhull algorithm is being thrown out of gear by sequences that have the same energy. An example of this situation is shown in Figure~\ref{fig:sim2_debug1}
\begin{figure}[h!]
    \centering
    \includegraphics[width=1.0\textwidth]{pics/sim2_debug1.pdf}
    \caption{This figure illustrates the issue when there are multiple sequences with the same energy. Here sequences 3 and 4 have the same energy. This causes the convex hull algorithm to fail in its current implementation.   }
    \label{fig:sim2_debug1}
\end{figure}
\pagebreak
